Matching ontologies with distributed word embeddings

### 2016-07-07 Paper/Draft.tex
Added acknowledgements

 \pagenumbering{roman}
 \section*{Acknowledgements}
 Arjen de Vries, professor at the Radboud University of Nijmegen and my mentor - Kennis enthusiasme en als het tegenzat kon hij me toch motiveren.
 Sanna Dinh, my partner - Nachtenlang opgebleven om het schrijfwerk en plaatjes
 Jeroen Vuurens, Delft University of Technology - Sparren over word2vec
 Xander Wilcke - Inspireren over het Semantisch Web
 Marianne - op de gekste tijdstippen skypen en proof-readen
 Suzan Verberne, professor at the Radboud University of Nijmegen - Nakijken
 Flynn, my pug - For the fresh air when I needed a minute to relax

@@

 \newpage
 \subsection{Interpretation}

>>>>

 \pagenumbering{roman}
 \section*{Acknowledgements}
 Arjen de Vries, professor at the Radboud University of Nijmegen and my mentor, for his limitless pool of knowledge and enthusiasm. For getting me out of the mud when I was stuck and motivating me to push on. Suzan Verberne, professor at the Radboud University of Nijmegen, for co-reading 
 Jeroen Vuurens, from Delft University of Technology, for helping me figure out Word2vec.
 Xander Wilcke, from the VU Amsterdam, for inspiring me to combine Machine Learning with the Semantic Web.
 Sanna Dinh, my partner, for spending countless hours in the night making this thesis readable and designing many of the images, making this thesis understandable.
 Marianne, my mother-in-law, for being available on Skype at the most unconventional times to advise and proof-read. Flynn, my pug - For the fresh air when I needed a minute to relax.

@@

 \newpage
 \subsection{Interpretation}
 %TODO interpretation
